\documentclass[smallheadings,12pt,a4paper, bibtotoc, abstracton, pointlessnumbers]{scrartcl}

%Pakete
\usepackage{PaketeEssays}
\usepackage{adjustbox}
%\input{classicthesis-config}
\makeatletter
\renewcommand*{\@fnsymbol}[1]{\ensuremath{\ifcase#1\or \dagger\or *\or  \ddagger\or
		\mathsection\or \mathparagraph\or \|\or **\or \dagger\dagger
		\or \ddagger\ddagger \else\@ctrerr\fi}}
\makeatother



\begin{document}
	
	
	\title{\Large{Routine Workers in a Digitalized World of Work: Evidence from Switzerland}}
	
	\author{\large
		Thomas Kurer\thanks{Weatherhead Center for International Affairs, Harvard University. \Chref{mailto:tkurer@wcfia.harvard.edu}{tkurer@wcfia.harvard.edu}.}
	}
	
	\date{\small{\today} \\ % Word Count: 4'436
	}
	\maketitle
	\begin{abstract}
		\noindent
		{\em
This paper explores the distributional consequences of technological change on mid-skilled routine workers in Switzerland in three steps: (1) The first part studies aggregate trends in the labor market and confirms the pattern of an eroding middle: The disadvantages of technological progress are concentrated on routine workers whose share in the labor force has drastically declined over time. (2) In order to better understand the economic conditions associated with this overall pattern, I draw on individual-level panel data to study actual employment transitions. The analysis shows that transitions are less frequent than the aggregate pattern might suggest: Only a minority of routine workers actually switches to other jobs while the largest chunk of the decline is explained by ``natural transitions" into retirement. (3) The last part of the paper draws on original survey data to examine routine workers' subjective assessment of their chances in a changing world of work and demonstrates a surprisingly high degree of consciousness about susceptibility to automation. To conclude, I discuss political and societal implications of the ``hollowing of the middle".

This is to add some content for the github class.

And here is another change, made online, from github.com. The idea is to then pull/push to remote machine.
		}

	\end{abstract}
\vspace{1cm}
Keywords: Employment Polarization, Technological Change, Routine Work, Middle Class.
	
	\thispagestyle{empty}




\end{document}
